\documentclass[]{chris_katsaras_resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Christopher}{Katsaras}{ \urlstyle{same}\url{http://chriskatsaras.com} | Github:// \href{https://github.com/ChrisKatsaras}{\custombold{chriskatsaras}}
| LinkedIn://  \href{https://www.linkedin.com/in/christopher-katsaras-0a326211a/}{\custombold{Christopher-Katsaras}} \href{mailto:chriskatsaras5@gmail.com}\\{16 Harrow Ct, Guelph, ON} | 519.820.5255
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hfill
\begin{minipage}[t]{1\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Camis}
\descript{| Full Stack Developer }
\location{Feb 2018 – Present | Guelph, ON}
\vspace{\topsep}
\begin{tightemize}\item Developed new features using a variety of languages / frameworks such as Angular, Typescript, Redux, Webpack and C\# .
\item Fixed bugs and refactored various pieces of functionality to ensure code quality was maintained. 
\item Developed unit tests using Karma and Jest.

\end{tightemize}
\sectionsep

\runsubsection{University of Guelph}
\descript{| Undergraduate Research Assistant }
\location{May 2017 – Aug 2017 | Guelph, ON}
\begin{tightemize}
\item Restructured database schema forthe Labrador Wellbeing project.\item Developed data visualizations for survey questions using Chart.js.\end{tightemize}
\sectionsep

\runsubsection{University of Guelph}
\descript{| Undergraduate Research Assistant }
\location{May 2016 – Aug 2016 | Guelph, ON}
\begin{tightemize}
\item Developed front-end for Farm to Fork, a food donation platform, using AngularJS and Angular-Material. \item Expanded system to work on a global scale. \end{tightemize}
\sectionsep

\runsubsection{University of Guelph}
\descript{| Undergraduate Teaching Assistant}
\descript{ Introduction to Programming / Computers in Society }
\location{Sep 2015 – Aug 2017 | Guelph, ON}
\begin{tightemize}
\item Led lab sessions and taught students introductory programming concepts in C.\item Assisted students in debugging their code as well as identifying how they could better
debug their own code in the future.\item Graded assignments, giving students detailed information on how they could improve
their coding style and logic.
\end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Swish Stats}
\descript{| https://swishstats.netlify.com }
\location{May 2018 – Present | \custombold{Tech Stack:} React, NextJS, Webpack, React Bootstrap, Netlify}
\vspace{2mm}
A progress web app that allows players to view and compare various NBA related statistics. 
Swish stats is still under development and is currently hosted on Netlify.
\sectionsep

\runsubsection{Stat Llama}
\location{Sep 2018 – Dec 2018 | \custombold{Tech Stack:} React, NodeJS, Webpack, React Semantic UI, Redux}
\vspace{2mm}
A progressive web app showcasing Fortnite store items, news and stats. Stat Llam has been archived and is not currently hosted.
\sectionsep

\runsubsection{Arnold Time}
\descript{| http://arnoldtime.com }
\location{June 2017 – Aug 2017 | \custombold{Tech Stack:} AngularJS, NodeJS, Angular Material, Socket.IO, Redis, Amazon Web Services}
\vspace{2mm}

A simple online multiplayer shooter. Arnold Time is hosted on Amazon Web Services with no future development work planned.
\sectionsep

\runsubsection{Dialog System Compiler}
\location{Jan 2015 – Apr 2015 | \custombold{Tech Stack:} C, Java, JNI, Lex/ Yacc, SQL}
\vspace{2mm}
Developed and IDE that translates simple config files into functional Java GUI’s. Two methods were to compile config files which included State-based parsing in C and Lex/Yacc. A Java IDE was developed in order to connect to a C based compiler using JNI.
\sectionsep

\section{Education} 

\subsection{University of Guelph}
\descript{Bachelor of Computing (Honours)}
\location{Completed Dec 2017 | Guelph, On }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2018         & Teaching Assistant Award &  School of Computer Science\\
2015-2017    & Dean's List  & Fall 2015 (84\%), Winter 2016 (84\%), Fall 2016 (84\%), Winter 2017 (84\%)\\
2016	     & Best poster in School of Computer Science & CPES poster competition \\

\end{tabular}

\end{minipage} 
\end{document}