\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Christopher}{Katsaras}{ \urlstyle{same}\url{http://chriskatsaras.com} | 
\href{mailto:chriskatsaras5@gmail.com}{16 Harrow Ct, Guelph, ON} | 519.820.5255
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Technical Skills}
\location{Languages}
\textbullet{} JavaScript / TypeScript \\ \textbullet{} C\# \\
\textbullet{} HTML/ CSS \\
\textbullet{} C\\
\sectionsep

\location{Frameworks / Libraries:}
\textbullet{} Anuglar / AngularJS\\
\textbullet{} NodeJS\\
\textbullet{} Webpack\\
\textbullet{} MySQL\\
\textbullet{} Redux\\
\textbullet{} Jest\\
\textbullet{} ASP.NET CORE\\
\sectionsep

\location{Tools:}
\textbullet{} Git\\
\textbullet{} AWS\\
\textbullet{} Netlify\\
\sectionsep

\location{Environments:}
\textbullet{} Windows\\
\textbullet{} Linux\\
\textbullet{} OSX\\
\sectionsep

\location{Software Engineering:}
\textbullet{} Scrum\\
\textbullet{} Agile\\
\textbullet{} Kanban\\
\sectionsep

\location{Familiar:}
\textbullet{} Python\\
\textbullet{} Java\\
\sectionsep
\sectionsep
\sectionsep

\subsection{Technical Skills}

\textbullet{} Teaching \\
\textbullet{} Team Leadership \\
\textbullet{} Public Speaking\\
\textbullet{} Time Management\\
\textbullet{} Academic Writing\\

\sectionsep
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Guelph}
\descript{Bachelor of Computing (Honours)}
\location{Completed Dec 2017 | Guelph, On }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/ChrisKatsaras}{\custombold{chriskatsaras}} \\
LinkedIn://  \href{https://www.linkedin.com/in/christopher-katsaras-0a326211a/}{\custombold{Christopher-Katsaras}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Camis}
\descript{| Full Stack Developer }
\location{Feb 2018 – Present | Guelph, ON}
\vspace{\topsep}
\begin{tightemize}\item Developed new features using a variety of languages / tools such as Angular, Typescript, Redux and C# .
\item Fixed bugs and refactored various pieces of functionality to ensure code quality was maintained. 
\item Developed unit tests using Karma and Jest.

\end{tightemize}
\sectionsep

\runsubsection{University of Guelph}
\descript{| Undergraduate Research Assistant }
\location{May 2017 – Aug 2017 | Guelph, ON}
\begin{tightemize}
\item Restructured database schema forthe Labrador Wellbeing project.\item Developed data visualizations for survey questions using Chart.js.\end{tightemize}
\sectionsep

\runsubsection{University of Guelph}
\descript{| Undergraduate Research Assistant }
\location{May 2016 – Aug 2016 | Guelph, ON}
\begin{tightemize}
\item Developed front-end for Farm to Fork, a food donation platform, using AngularJS and Angular-Material. \item Expanded system to work on a global scale. \end{tightemize}
\sectionsep

\runsubsection{University of Guelph}
\descript{| Undergraduate Teaching Assistant}
\descript{ Introduction to Programming / Computers in Society }
\location{Sep 2015 – Aug 2017 | Guelph, ON}
\begin{tightemize}
\item Led lab sessions and taught students introductory programming concepts in C.\item Assisted students in debugging their code as well as identifying how they could better
debug their own code in the future.\item Graded assignments, giving students detailed information on how they could improve
their coding style and logic.
\item Led class discussions about the impact of technology on society.\end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Swish Stats}
\descript{| https://swishstats.netlify.com }
\location{May 2018 – Present | Guelph, ON}
A progress web app that allows players to view and compare various NBA related statistics. Developed using React, NextJS, Webpack & React Bootstrap.
Project is currently under development
\sectionsep

\runsubsection{Arnold Time}
\descript{| http://arnoldtime.com }
\location{June 2017 – Aug 2017 | Guelph, ON}
An online shooter developed using NodeJS, AngularJS, Angular Material and Redis.
\sectionsep

\runsubsection{Dialog System Compiler}
\location{Jan 2015 – Apr 2015 | Guelph, ON}
Developed and IDE that translates simple config files into functional Java GUI’s. Two methods were to compile config files which included State-based parsing in C and Lex/Yacc. A Java IDE was developed in order to connect to a C based compiler using JNI.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2018         & Teaching Assistant Award &  School of Computer Science\\
2017	     & Dean's List   & Winter 2017 Semester | 89\%\\
2016	     & Best poster in School of Computer Science & CPES poster competition \\
2016	     & Dean’s list & Winter 2016 semester| 89\%\\
2016	     & Dean’s list & Fall 2016 semester| 87\%\\
2015	     & Dean’s list & Fall 2015 semester| 84\%\\
\end{tabular}

\end{minipage} 
\end{document}